---
title: "Use of the (updated) powers package"
author: "Caroline Seip"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Use of the (updated) powers package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

#Introduction

The `powers` package was developed by Vincenzo Coia. I have added the `inchtocm` function to this package.

#Load package

Start by loading the `powers` package:
```{r}
suppressPackageStartupMessages(library(powers))
```

#Examples 

The powers package includes functions to...

Square a vector, using `square`:

```{r}
square(2)
```

Cube a vector, using `cube`:

```{r}
cube(3)
```

Take the reciprocal of a vector, using `reciprocal`:

```{r}
reciprocal(4)
```

Convert inches to centimetres, using `inchtocm`:

```{r}
inchtocm(12)
```

These functions can also be applied to a list of vectors, check it out:
```{r}
mylist <- list(1:10)
lapply(mylist, inchtocm)
```

How fun!
